Untitled

### 2022-07-04 Main_Figures/Figure3.Rmd
edits

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1.rds")
########################################################################################################################

@@

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend.   High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+ggtitle("(e)")

@@

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles      Long styles\n High poll. depend.   Low poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"))+ 
  scale_color_manual(name="Functional groups",values=c("orange", 
  "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_log10()+ggtitle("(f)")

>>>>

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab(NULL)+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab(NULL)+ xlab(NULL)+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab(NULL)+ xlab(NULL)+
  theme_ms() + theme(legend.position = "none") + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1.rds")
########################################################################################################################

@@

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab(NULL)+ xlab("Low poll. depend.   High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+ggtitle("(e)")

@@

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab(NULL)+ xlab("Short styles      Long styles\n High poll. depend.   Low poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold"))+ 
  scale_color_manual(name="Functional groups",values=c("orange", 
  "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_log10()+ggtitle("(f)")

### 2022-07-04 Manuscript/Lanuza_et_al_2022.Rmd
edits

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)")

@@

>>>>

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)") +
    xlab(NULL) + ylab(NULL)

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)") +
    xlab(NULL) + ylab(NULL)

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL)

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=28,out.width="90%",fig.align='center',fig.cap="\\textbf{Fig. S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows). The x-axis shows the most illustrative trait extremes of the trait continuum. Note that the plots are coloured by the different network metrics.", fig.pos= "h"}

#library(brms) #modelling
library(cowplot) #panel of plots
library(ggplot2) #plotting
library(patchwork)

setwd("~/Dropbox/PhD/R/Chapter_2")

#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs

plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")

plot_metrics_pcs

### 2022-07-04 Manuscript/Lanuza_et_al_2022.tex
edits

@@

The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence \href{}{que opinas de que pol dep salga en dos ejes? No es raro?}. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{16},\protect\hyperlink{ref-carmona2021}{18}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}. Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds. However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, to better capture the strength of these mutualistic interactions at a macroecological scale.

>>>>

\begin{figure}[h]

{\centering \includegraphics[width=0.9\linewidth]{output/figures/unnamed-chunk-5-1}

\caption{\textbf{Fig. S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows). The x-axis shows the most illustrative trait extremes of the trait continuum. Note that the plots are coloured by the different network metrics.}\label{fig:unnamed-chunk-5}
\end{figure}

@@

The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{16},\protect\hyperlink{ref-carmona2021}{18}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}. Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds. However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, to better capture the strength of these mutualistic interactions at a macroecological scale.

### 2022-07-04 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
edits

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=28}

@@

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(3.5)),
           axis.text=element_text(size = rel(2.75), color = "black"),
           plot.title = element_text(size = 40,face="bold"),
           legend.title=element_text(face="bold"),
           legend.text=element_text(),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(0.4, 'lines'),
           panel.border=element_rect(color="black",size=3),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank()
     ))
}
#########

@@

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = Visits),
  size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")+ggtitle("A")

@@

Visits_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = Visits),
  size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC2")+ggtitle("B")

@@

Visits_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = Visits),
  size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC3") +ggtitle("C")

@@

normalised.degree_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = normalised.degree),
  size = 3, alpha=0.65, colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1")+ggtitle("D")

@@

normalised.degree_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = normalised.degree),
  size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC2")+ggtitle("E")

@@

normalised.degree_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = normalised.degree),
  size = 3, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC3")+ggtitle("F")

@@

Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
  size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1")+ggtitle("G")

@@

Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
  size = 3, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC2")+ggtitle("H")

@@

Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
 size = 3, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC3")+ggtitle("I")

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=22, fig.width=28, fig.align='center'}

@@

# Theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2.2)),
           axis.text=element_text(size = rel(1.9), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.7)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.9, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(3.05),face="bold"),
           plot.subtitle = element_text(face="bold",size=rel(2.7))
     ))
}
#########

@@

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = Visits),
  size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("Sum of visits") + xlab("PC1")+ggtitle("PC1", subtitle = "(a)")+ xlab(NULL)

@@

Visits_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = Visits),
  size = 3, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab("") + xlab("PC2")+ggtitle("PC2", subtitle = "(b)")+ xlab(NULL)

@@

Visits_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = Visits),
  size = 3.5, alpha=0.65, colour="goldenrod3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC3") +ggtitle("PC3", subtitle = "(c)")+ xlab(NULL)

@@

normalised.degree_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = normalised.degree),
  size = 3.5, alpha=0.65, colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab("Normalized degree") + xlab("PC1") + ggtitle(NULL, subtitle = "(d)")+ xlab(NULL)

@@

normalised.degree_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = normalised.degree),
  size = 3.5, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab(NULL) + xlab("PC2") + ggtitle(NULL, subtitle = "(e)")+ xlab(NULL)

@@

normalised.degree_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = normalised.degree),
  size = 3.5, alpha=0.65,colour="aquamarine4") + geom_line(colour="black",size=1.5)  +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.25,fill="black") + ylab(NULL) + xlab("PC3") + ggtitle(NULL, subtitle = "(f)")+ xlab(NULL)

@@

Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1") + ggtitle(NULL, subtitle = "(g)") +  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")

@@

Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC2") + ggtitle(NULL, subtitle = "(h)") + xlab("Low poll. depend.   High poll. depend.")

@@

Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
 size = 3.5, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC3") + ggtitle(NULL, subtitle = "(i)")+ xlab("Short styles      Long styles\n High poll. depend.   Low poll. depend.")
